Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-03-31 inspiral_svd.tex
more focus on multimessenger astronomy and early warning, added acks
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@706 ccdd05d5-56c1-461a-bf98-85f6876523b4

\documentclass[showpacs,groupedaddress,showkeys,preprintnumbers]{iopart}
\input{packages}
\input{macros}

@@

\title[LLOID]{Towards realtime detection of compact binary coalescence to
improve the prospects for multimessenger astronomy\editorial{Submit to PRD or
CQG?}}

@@

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors offers a unique opportunity for multimessenger
Astronomy.  Prompt alerts to the Astronomical community will assure that all
available instruments are observing the electromagnetic counterparts to the
first gravitational waves from coalescing compact objects.   Rapid, near
realtime alerts, will improve the chances of detecting weak, decaying
electromagnetic signals and correlating such signals with the gravitational
wave strain.  In this paper, we describe a new, near realtime, detection
strategy that exploits the properties of inspiral waveforms using principal
component analysis, multi-rate filtering, and hierarchical detection.  We
provide receiver operating characteristics from a prototype search pipeline
that is capable of near-realtime detection with acheivable computational
requirements.  
\editorial{CH: I wasn't happy with the tone of the abstract.  I want to
focus on the science goal of multimessenger Astronomy.}
\end{abstract}

@@

\ack{\textsc{ligo} was constructed by the California Institute of Technology
and Massachusetts Institute of Technology with funding from the National
Science Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}. This paper has \textsc{ligo} Document
Number \textsc{ligo}-\textsc{p}\oldstylenums{0900004}-v\oldstylenums{3}.}

\appendix
\input{appendix}

>>>>

\documentclass[showpacs,groupedaddress,showkeys,preprintnumbers]{iopart}
\input{packages}
\input{macros}
\renewcommand{\arraystretch}{1.2}

@@

\title[LLOID]{Improving the prospects for multimessenger astronomy with
\earlywarning\ detection of compact binary coalescence.}

@@

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors offers a unique opportunity for multimessenger
Astronomy.  Prompt alerts to the Astronomical community will assure that all
available instruments are observing the electromagnetic counterparts to the
first gravitational waves from coalescing compact objects.   Rapid, near
realtime alerts, will improve the chances of detecting weak, decaying
electromagnetic signals and correlating such signals with the gravitational
wave strain.  In this paper, we describe a new, realtime, detection strategy
that exploits the properties of inspiral waveforms using principal component
analysis and multi-rate filtering.  We provide detection efficiency
characteristics from a prototype search pipeline that is capable of
\earlywarning\ detection with acheivable computational requirements.  
\end{abstract}

@@

\ack{\LIGO\ was constructed by the California Institute of Technology
and Massachusetts Institute of Technology with funding from the National
Science Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}. CH would like to thank Ilya Mandel
for many discussions about rate estimates and the prospects of early
detection.

This paper has \LIGO\ Document
Number \LIGO-\textsc{p}\oldstylenums{0900004}-v\oldstylenums{3}.}

%\appendix
%\input{appendix}
